Brief Announcement: An Improved Lower Bound for Dynamic Balanced Graph Partitioning

### 2020-02-14 paper/paper.tex
hiding comment
fixing \TAlg

\usepackage[utf8]{inputenc}
\usepackage{xspace}
\usepackage{balance}
\usepackage{amsmath,amssymb,amsfonts,mathtools,amsthm}
\usepackage[noend]{algpseudocode}
\usepackage{algorithm}

@@

\newcommand{\OPT}{\mathit{OPT}}
\newcommand{\ALG}{ALG}
\newcommand{\OBRP}{BRP}
\newcommand{\PPOBRP}{PP-BRP}
\newcommand{\TAlg}{{\ensuremath{ALG_{k=3}}}\xspace} % we should change this name

@@

\begin{proof}
	We construct an instance of the problem with $\ell$ clusters 
	$\set{ S_1, S_2,\dots , S_{\ell}}, |S_i|  = k$.
	Let $I(C)$ denote the cluster where nodes in a component $C$ are located initially.
	\maciek{So far components were not introduced; the best place to introduce these would be around the definition of \PPOBRP}.
	Fix any online algorithm \ALG{}.
	We construct the input sequence of requests for \ALG{} as follows.
	First,
	we issue $k-2$ (internal) requests so that \ALG{} can form a component of $k-1$
	nodes on the cluster $S_1$.
	Recall that internal requests does not incur any cost for \ALG{}.
	If \ALG{} at any point splits a component
	(i.e., spreads its nodes over two or more clusters),
	then we continue to issue requests between non-collocated nodes of the component until \ALG{} collocates the nodes of the component.
	If \ALG{} never collocates them then it is not competitive.

@@

  We define the algorithm \TAlg in the following way.
  \TAlg maintains components for each node.
  Intially, each node is in its own singleton component.
  For each pair of nodes \TAlg maintains a counter, initiated $0$, and upon receiving a request to this pair while its nodes are located on different servers, it increases the counter by $1$.
  If a counter for a pair $(u,v)$ reaches $\alpha$, \TAlg merges the components of $u$ and $v$, and moves to the closest partition, where it each component has all of its nodes in one server.
  If no such partition exists, \TAlg resets all components to singletons and all counters to $0$.

@@

  We say that \TAlg is \emph{component respecting}, i.e., it maintaints the invariant that nodes of each component are located at the same server.

@@

      Finally, we consider the case where both $U$ and $V$ are $C_2$. Note that $(u,v)$ cannot both belong to a component of size $2$, as this would mean that \TAlg has the component of size $4$, a contradiction with the case assumption that the component-respecting partition exists. 
      If either $u$ or $v$ belongs to a component of size $2$ then it suffices to exchange components of size $1$ between $U$ and $V$.
      Finally, if $u$ and $v$ belong to components of size $1$, then we must place them in a cluster different from $U$ and $V$.
      Note that in such case, a $C_1$-type cluster $W$ exists, as otherwise the input graph would not have a perfect partition. In this case GREEDY exchanges the nodes $u$ and $v$ with any two nodes of $W$, for the total cost of $2\cdot \alpha$.
  \end{proof}

  \begin{theorem}
    \TAlg is $O(\ell)$-competitive.
  \end{theorem}
  \begin{proof}
    Consider a request $(u,v)$.
    If $u$ and $v$ are collocated in the same server, then \TAlg pays nothing.

    \TAlg collocates nodes belonging to one component, hence during a single phase, we have at most $2\cdot \ell$ requests to non-collocated nodes.
    We use Lemma~\ref{lem:1req} to bound the cost of each such request, and therefore \TAlg pays $6\cdot\alpha\cdot \ell$ in a single phase.
    On the other hand, during each phase, OPT pays at least $1$.
  \end{proof}

>>>>

\usepackage[utf8]{inputenc}
%\usepackage{xspace}
\usepackage{balance}
\usepackage{amsmath,amssymb,amsfonts,mathtools,amsthm}
\usepackage[noend]{algpseudocode}
\usepackage{algorithm}

@@

\newcommand{\OPT}{\mathit{OPT}}
\newcommand{\ALG}{ALG}
\newcommand{\OBRP}{BRP}
\newcommand{\PPOBRP}{PP-BRP}
\newcommand{\TAlg}{{\ensuremath{ALG_{k=3}}}} % we should change this name

@@

\begin{proof}
	We construct an instance of the problem with $\ell$ clusters 
	$\set{ S_1, S_2,\dots , S_{\ell}}, |S_i|  = k$.
	Let $I(C)$ denote the cluster where nodes in a component $C$ are located initially.
%	\maciek{So far components were not introduced; the best place to introduce these would be around the definition of \PPOBRP}.
	Fix any online algorithm \ALG{}.
	We construct the input sequence of requests for \ALG{} as follows.
	First,
	we issue $k-2$ (internal) requests so that \ALG{} can form a component of $k-1$
	nodes on the cluster $S_1$.
	Recall that internal requests does not incur any cost for \ALG{}.
	If \ALG{} at any point splits a component
	(i.e., spreads its nodes over two or more clusters),
	then we continue to issue requests between non-collocated nodes of the component until \ALG{} collocates the nodes of the component.
	If \ALG{} never collocates them then it is not competitive.

@@

  We define the algorithm \TAlg{} in the following way.
  \TAlg{} maintains components for each node.
  Intially, each node is in its own singleton component.
  For each pair of nodes \TAlg{} maintains a counter, initiated $0$, and upon receiving a request to this pair while its nodes are located on different servers, it increases the counter by $1$.
  If a counter for a pair $(u,v)$ reaches $\alpha$, \TAlg{} merges the components of $u$ and $v$, and moves to the closest partition, where it each component has all of its nodes in one server.
  If no such partition exists, \TAlg{} resets all components to singletons and all counters to $0$.

@@

  We say that \TAlg{} is \emph{component respecting}, i.e., it maintaints the invariant that nodes of each component are located at the same server.

@@

      Finally, we consider the case where both $U$ and $V$ are $C_2$. Note that $(u,v)$ cannot both belong to a component of size $2$, as this would mean that \TAlg{} has the component of size $4$, a contradiction with the case assumption that the component-respecting partition exists. 
      If either $u$ or $v$ belongs to a component of size $2$ then it suffices to exchange components of size $1$ between $U$ and $V$.
      Finally, if $u$ and $v$ belong to components of size $1$, then we must place them in a cluster different from $U$ and $V$.
      Note that in such case, a $C_1$-type cluster $W$ exists, as otherwise the input graph would not have a perfect partition. In this case GREEDY exchanges the nodes $u$ and $v$ with any two nodes of $W$, for the total cost of $2\cdot \alpha$.
  \end{proof}

  \begin{theorem}
    \TAlg{} is $O(\ell)$-competitive.
  \end{theorem}
  \begin{proof}
    Consider a request $(u,v)$.
    If $u$ and $v$ are collocated in the same server, then \TAlg{} pays nothing.

    \TAlg{} collocates nodes belonging to one component, hence during a single phase, we have at most $2\cdot \ell$ requests to non-collocated nodes.
    We use Lemma~\ref{lem:1req} to bound the cost of each such request, and therefore \TAlg{} pays $6\cdot\alpha\cdot \ell$ in a single phase.
    On the other hand, during each phase, OPT pays at least $1$.
  \end{proof}
